An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
prop 7

\begin{proposition}\label{prop:SL-minimum}
  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.\raft{Let's change to ``finite representive set''}
  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
\end{proposition}
\begin{proof}
	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.

@@

\begin{lemma}\label{lem:finite-minrep-weakly-dominate}
	Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
	For any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite minimum representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
	Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ on exactly the level set.
	Since $E_L$ is a convex polyhedron in $\reals^{n+1}$, we can take a linear projection of the faces of $E_L$ onto $\simplex \subset \reals^n$ to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
	Thus, every level set of $\Gamma$ is a cell in the induced power diagram.

	Observe that any $r^* \in \R^*$ must be a full-dimensional cell of the power diagram, since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
	Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
	If $\Gamma_r$ is not full-dimensional, it must be a face of some full-dimensional level set $\Gamma_{r^*}$, and therefore $\Gamma_r \subset \Gamma_{r^*}$.
\end{proof}

@@

$1 \Rightarrow 2$:
Since $\Gamma$ embeds a finite property $\gamma$ with minimum representative set $\Sc$, $\Gamma$ also has a finite minimum representative set $\U := \varphi(\Sc)$.
We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \{\gamma_r \mid r \in \Sc \}$, and the result follows from $\U$ being a finite minimum representative set.
Since $\U$ is a finite minimum representative set, $\trimnonred(\Gamma) \supseteq \{\Gamma_u \mid u \in \U\}$ follows immediately.
We now show $\trimnonred(\Gamma) \subseteq \{\Gamma_u \mid u \in \U\}$.
Consider any $\Gamma_{u'} \in \trimnonred(\Gamma)$.
Since $\Gamma$ has the finite minimum representative set $\U$, if $u' \not \in \U$, there is some $u \in \U$ such that $\Gamma_{u'} \subseteq \Gamma_u$ by Lemma~\ref{lem:finite-minrep-weakly-dominate}. 
If $\Gamma_{u'} \subsetneq \Gamma_u$, then $u' \not \in \U_\equiv$, and $\Gamma_{u'} \not \in \trimnonred(\Gamma)$ nor is $u' \in \U$.
If $\Gamma_{u'} = \Gamma_u$, then$u' \equiv u$ so $\Gamma_{u'} \in \trimnonred(\Gamma)$ as $[u'] = [u] \in \U_\equiv$.
Thus, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, so $\trimnonred(\Gamma)$ is finite and unions to the simplex.

>>>>

\begin{proposition}\label{prop:SL-minimum}
  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.\raft{Chengaed to ``finite representive set''}
  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
\end{proposition}
\begin{proof}
	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.

@@

\begin{lemma}\label{lem:finite-minrep-weakly-dominate}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
  For any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
  Moreover, the level sets $\{\Gamma_{r^*} \mid r^* \in \R^*\}$ are the unique full-dimensional level sets of $\Gamma$.
\end{lemma}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite minimum representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
  Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ exactly when $p\in\Gamma_r$.
  Since $E_L$ is a convex polyhedron in $\reals^{n+1}$, we can take a linear projection of the faces of $E_L$ onto $\simplex \subset \reals^n$ to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
  Thus, every level set of $\Gamma$ is a cell in the induced power diagram.

  By Proposition~\ref{prop:SL-minimum}, the level sets $\{\Gamma_{r^*} \mid r^*\in\R^*\}$ are exactly the projections of the facets of $E_L$, and thus exactly the full-dimensional cells of the induced power diagram.
  % , since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
  % Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
  For any $r\in\R$, the level set $\Gamma_r$ is a cell of the induced power diagram, and thus contained in some full-dimensional cell $\Gamma_{r^*}$.
\end{proof}
\begin{corollary}\label{cor:finite-minrep-trim}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
  Then $\trimnonred(\Gamma) = \{\Gamma_r \mid r\in\R^*\}$.
\end{corollary}
\begin{proof}
  Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
  Let $r\in\R$ be arbitrary.
  From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
  In the first case, $\Gamma_r$ is an element of both $\trimnonred(\Gamma)$ and $\Theta$, and in the second, $\Gamma_r$ is an element of neither (by definition of $\trimnonred$ and minimum representative).
  Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
\end{proof}

@@

$1 \Rightarrow 2$:
Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
If $\Gamma$ embeds $\gamma$ with map $\varphi$, then $\Gamma$ also has a finite representative set $\U := \varphi(\Sc)$ and $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
\raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.
